---
title       : BMI Calculator
subtitle    : Part of Data Products Course
author      : Alexandre Gabriel
job         : BI Specialist
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Slide 2

This is a presentation to show:
- What the BMI calculator does;
- ui.R code;
- server.R code.

I will post the .R codes here given I didn't find out where I could put them when submitting my project.

--- .class #id 

## Slide 3

The BMI calculator takes 2 inputs (height in meters and weight in kilograms) and calculates the BMI (Body Mass Index) given those two values.

The BMI formula is weight/(height*height).

For instance, in my case, I have 1.85m and weight 120kg. So my BMI is

```{r}
height <- 1.85
weight <- 120
bmi <- weight/(height*height)
bmi
```

--- .class #id 

## Slide 4

ui.R code:

```{r eval=FALSE}
library(shiny)
shinyUI(pageWithSidebar(
  headerPanel ("BMI Calculator"),
  sidebarPanel(
    h3('Instructions'),
    p('Enter the height (in cm), and weight (in kg).  
      The calculated BMI will be shown to the right.'),
    h3('Please enter predictors of BMI below.'),
    numericInput(inputId = "height", label = 'Height (cm)', value = 170),
    numericInput(inputId = "weight", label = 'Weight (kg)', value = 80) ),
  mainPanel(
    p('Height'), textOutput("height"),
    p('Weight'), textOutput("weight"),
    p('BMI'), textOutput("result")
  )
))
```

--- .class #id 

## Slide 5

server.R code:

```{r eval=FALSE}
library(shiny)
shinyServer(
  function(input,output) {
    output$height <- renderText(input$height) 
    output$weight <- renderText(input$weight)
    #10000 below because height was given in centimeters
    output$result <- reactive({input$weight/(input$height*input$height/10000)})
  }
)
```


